Calculating Entropies With Nested Sampling

### 2017-01-15 paper/ms.tex
Walter reference

>>>>

\subsection{The sequence of $X$ values}
When $N=1$, the sequence of $X$ values is a Poisson process.

\citet{Walter2015} showed how this property can be used to construct a
version of NS that produces unbiased estimates of the marginal likelihood.
However, it can be used to construct an unbiased estimator of
a log-probability, which is more relevant to information theoretic
quantities.

\subsection{}
